
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```

<style type="text/css">

div.icon-row {
  width: 910px;
  height: 150px;
  margin: 40px 0
}
div.icon-row:after {
  content: "";
  display: table;
  clear: both;
}
div.icon-box {
  width: 220px;
  height: 150px;
  float: left;
  text-align: center;
}
a.icon {
  display: block;
  width: 80px;
  height: 80px;
  border-radius: 40px;
  border: solid 1px #467fbf;
  text-align: center;
  padding: 20px;
  margin: 0 auto 10px auto;
  transition: all 0.2s ease-out;
}
a.icon:hover {
  transform: scale(1.1, 1.1);
}
h3.icon-title {
  font-weight: bold;
  font-size: 15px;
}
i.fa {
  font-size: 35px;
  color: #467fbf;
}
div.last  {
  clear: both;
}
</style>

# quanteda: Quantitative Analysis of Textual Data

```{r eval = TRUE, message = FALSE, echo = FALSE, results = 'asis'}
unlink('index_cache', recursive = TRUE)
html <- readLines("pkgdown/icon.html")
html <- stringi::stri_replace_first_regex(html, "^\\s+", "")
cat(html, sep = "\n")
```


## About

An R package for managing and analyzing text, created by [Kenneth Benoit](http://kenbenoit.net).
Supported by the European Research Council grant ERC-2011-StG 283794-QUANTESS.


## How to Install

The normal way from CRAN, using your R GUI or 
```{r eval = FALSE}
install.packages("quanteda") 
```

Or for the latest development version:
```{r eval = FALSE}
# devtools package required to install quanteda from Github 
devtools::install_github("quanteda/quanteda") 
```

Because this compiles some C++ and Fortran source code, you will need to have installed the appropriate compilers.

**If you are using a Windows platform**, this means you will need also to install
the [Rtools](https://CRAN.R-project.org/bin/windows/Rtools/) software available
from CRAN.  

**If you are using macOS**, you should install the 
[macOS tools](https://cran.r-project.org/bin/macosx/tools/), 
namely the Clang 6.x compiler and the GNU Fortran compiler (as **quanteda** requires gfortran to build).
    

## How to Use 

See the [quick start guide](http://docs.quanteda.io/articles/quickstart.html) to learn how to use **quanteda**.

## Leaving Feedback

If you like **quanteda**, please consider leaving [feedback or a testimonial here](https://github.com/quanteda/quanteda/issues/461).

## Contributing

Contributions in the form of feedback, comments, code, and bug reports are most welcome.  How to contribute:

*  Fork the source code, modify, and issue a [pull request](https://help.github.com/articles/creating-a-pull-request-from-a-fork/) through the [project GitHub page](https://github.com/quanteda/quanteda).  See our [Contributor Code of Conduct](https://github.com/quanteda/quanteda/blob/master/CONDUCT.md) and the all-important **quanteda** [Style Guide](https://github.com/quanteda/quanteda/wiki/Style-guide).
*  Issues, bug reports, and wish lists: [File a GitHub issue](https://github.com/quanteda/quanteda/issues).
*  Usage questions:  Submit a question on the [**quanteda** channel on StackOverflow](https://stackoverflow.com/questions/tagged/quanteda).
*  Contact [the maintainer](mailto:kbenoit@lse.ac.uk) by email.

